Verifying Demonstrations

### 2017-08-25 properties.tex
Minor edits
Merges ideas with figure slide, adds transitive trust

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification 
    of the event.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

@@

  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}
\end{frame}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
      \item If included before \(t_e\), then it was created before \(t_e\).
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}, (\(t_s\) in the figure).
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}

>>>>

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

@@

  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<2>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

@@

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's and Bob's proofs.

      \item Physical transportation is limited.
      \item Accuracy of Alice's witnessing is proportional to time from Jane's 
        witnessing.
    \end{itemize}
  \end{idea}

  \begin{remark}
    \begin{itemize}
      \item Alice's signature key must have the physical travel properties, 
        embedded in hardware.
      \item Alice's witness signature must depend on Jane's.
      \item High-precision relation to time?
    \end{itemize}
  \end{remark}
\end{frame}
}

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane attends the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}
